---
title: "Exercise: Durbin-Watson Test Application in R"
author: "Dr. BENGHALEM Abdelhadi"
output:
  html_notebook:
    toc: yes
    fig_caption: yes
    theme: journal
  pdf_document:
    toc: yes
    editor_options:
  chunk_output_type: inline
---

Exercise: Durbin-Watson Test Application in R

Objective: To apply the Durbin-Watson test in R to assess autocorrelation in the residuals of a linear regression model.

Instructions:

1.  Load the necessary R packages.

2.  Import the mtcars dataset.

3.  Fit a linear regression model using the **`lm()`** function, with mpg as the response variable and disp and wt as the explanatory variables.

4.  Perform the Durbin-Watson test using the **`dwtest()`** function from the "lmtest" package.

5.  Interpret the results of the Durbin-Watson test

install.packages("lmtest")install.packages("lmtest")

```{r}
# Load required packages
library(lmtest)
```

```{r}
# Import dataset
data(mtcars)
```

```{r}
head(mtcars)
```

```{r}
class(mtcars)
```

```{r}
# Fit linear regression model
model <- lm(mpg ~ disp + wt, data = mtcars)
summary(model)
```

```{r}
durbin_watson <- dwtest(model)
```

```{r}
dwtest(model)
```

```{r}
# Interpret results
if (durbin_watson$p.value < 0.05) {
  cat("Autocorrelation detected. Consider model modification or alternative regression methods.")
} else {
  cat("No significant autocorrelation detected.")
}

```

From the output we can see that the test statistic is **1.2766** and the corresponding p-value is **0.01**. Since this p-value is less than 0.05, we can reject the null hypothesis and conclude that the residuals in this regression model are autocorrelated.
